Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-03-08 WSSSPE4_report/wg_letters.tex

\begin{itemize}
\item The Computing Research Association has produced a ``Best
  practices memo'' on the issue \cite{PSU99}. Among other points,
  the memo also clarified that conference proceedings are
  \textit{the} venue in Computer Science, and this has been used to
  convince deans and provosts of the value of these proceedings
  publications. The article may serve as a template for computational
  science.
\item The National Science Foundation has produced a number of ``Dear
  Colleague'' letter that consider the issue of software and, taken
  together, define a ``product'' for the purposes of
  2-page biosketches in a way that does not include only publications, but also
  software.%
  \footnote{The most pertinent such letter is
    \href{https://www.nsf.gov/pubs/2014/nsf14059/nsf14059.jsp}{NSF
      14-059, ``Dear Colleague Letter - Supporting Scientific
      Discovery through Norms and Practices for Software and Data
      Citation and Attribution''}.}
  This definition is ultimately codified in the National Science
  Foundation's ``Proposal and Award Policies and Procedures Guide''
  (often abbreviated as GPG) which in 2013 renamed the
  ``Publications'' section of 2-page biosketches to ``Products'' (see
  Chapter II.C.2.f(i)(c)) and now explicitly allows software to be
  referenced in this section.
\item There is also a 1995 report by the National Academies about
  Computer Science that addresses some of these issues, specifically
  on how writing software should be considered in comparison to more
  theoretical research \cite{NRC-careers-94}. 
\end{itemize}

>>>>

\begin{itemize}
\item The Computing Research Association has produced a ``Best
  practices memo'' on the issue \cite{PSU99}. Among other points,
  the memo also clarified that conference proceedings are
  \textit{the} venue in Computer Science, and this has been used to
  convince deans and provosts of the value of these proceedings
  publications. The article may serve as a template for computational
  science.
\item The National Science Foundation has produced a number of ``Dear
  Colleague'' letter that consider the issue of software and, taken
  together, define a ``product'' for the purposes of
  2-page biosketches in a way that does not include only publications, but also
  software.%
  \footnote{The most pertinent such letter is NSF
      14-059, ``Dear Colleague Letter - Supporting Scientific
      Discovery through Norms and Practices for Software and Data
      Citation and Attribution''~\cite{nsf-dcl-citation}.}
  This definition is ultimately codified in the National Science
  Foundation's ``Proposal and Award Policies and Procedures Guide''
  (often abbreviated as GPG) which in 2013 renamed the
  ``Publications'' section of 2-page biosketches to ``Products'' (see
  Chapter II.C.2.f(i)(c)) and now explicitly allows software to be
  referenced in this section.
\item There is also a 1995 report by the National Academies about
  Computer Science that addresses some of these issues, specifically
  on how writing software should be considered in comparison to more
  theoretical research \cite{NRC-careers-94}. 
\end{itemize}
